
read.csv() reads csv file into the data frame that it creates called studentSurvey.
Input: File path, header=TRUE specifies that data contains a header row and sep="," specifies that data is separated by commas.
Output: 
```{r}
studentSurvey<-read.csv(file="C:/Study/693/CombinedSurvey.csv", header=T, sep=",")
```


// PreMobDevelopment: Interested in mobile development.
```{r}
library(psych)
describeBy(studentSurvey$PreMobDevelopment, studentSurvey$Gender)
```


// PreWebDevelopment: Interested in web development.
```{r}
describeBy(studentSurvey$PreWebDevelopment, studentSurvey$Gender)
```


// PreDevelopingTools: Interested in developing tools.
```{r}
describeBy(studentSurvey$PreDevelopingTools, studentSurvey$Gender)
```


// PreCommercialProduct: Interested in developing a commercial product.
```{r}
describeBy(studentSurvey$PreCommercialProduct, studentSurvey$Gender)
```


// PreServeSchool: Interested in serving a school.
```{r}
describeBy(studentSurvey$PreServeSchool, studentSurvey$Gender)
```


// PreServeLocal: Interested in serving a local community.
```{r}
describeBy(studentSurvey$PreServeLocal, studentSurvey$Gender)
```


// PreServeIntenational: Interested in serving a national/international communities.
```{r}
describeBy(studentSurvey$PreServeIntenational, studentSurvey$Gender)
```


// PreMobDevExp: Confident and Experienced in Mobile Development.
```{r}
describeBy(studentSurvey$PreMobDevExp, studentSurvey$Gender)
```


// PreWebDevExp: Confident and Experienced in Web Development.
```{r}
describeBy(studentSurvey$PreWebDevExp, studentSurvey$Gender)
```


// PreEmbSystemsExp: Confident and Experienced in Desktop or Embedded Systems Development.
```{r}
describeBy(studentSurvey$PreEmbSystemsExp, studentSurvey$Gender)
```


// PreCSInnovate: Computer Science and Software Engineering are fields that further
// innovate in science and technology.
```{r}
describeBy(studentSurvey$PreCSInnovate, studentSurvey$Gender)
```


// PreCSHelpPeople: Computer Science and Software Engineering are fields that help people.
```{r}
describeBy(studentSurvey$PreCSHelpPeople, studentSurvey$Gender)
```


// PreInterestUse: Project Prefernce motivated by product being used by many people.
```{r}
describeBy(studentSurvey$PreInterestUse, studentSurvey$Gender)
```


// PreInterestWellKnown: Project Prefernce motivated by product becoming well known to
// people.
```{r}
describeBy(studentSurvey$PreInterestWellKnown, studentSurvey$Gender)
```


// Get total count of female and male
```{r}
table(studentSurvey$Gender)
```


// Get total count of different project categories selected by students as their first choice.
```{r}
table(studentSurvey$CategoryForFirstChoice)
```








