---
title: "Summer Research 2017"
author: 'William Zamora'
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{floatrow}
---
Will be using the libary psych to look at the data.
Read in data and store it surveyDataSummer2017 variable also ignored the word DK in the data.
```{r}
library(psych)
surveyDataSummer2017 <- read.csv(file="C:/Users/william/Desktop/SEER-SurveyAnalysis/TechStartupSummer2017.csv", header=T, sep=",")
surveyDataSummer2017[surveyDataSummer2017 == "DK"] <- NA
```

Created a new column, ProjectType, which categorizes the projects.
```{r}
surveyDataSummer2017$ProjectType[surveyDataSummer2017$PostProject%in% c("BossyUI", "BossyUI ")] <- "LFOSS"
surveyDataSummer2017$ProjectType[surveyDataSummer2017$PostProject%in% c("Hack N Slash", "TopJam","Big League Coders", "Smart Laser Tag", "DnD", "GNOME Accessibility", "Ushahidi")]<- "Toy"
surveyDataSummer2017$ProjectType[surveyDataSummer2017$PostProject%in% c("Better RQM", "Greatest RQM", "Automated User Tracking System", "AUTSNoon", "AUTSOne")] <- "Industry"
surveyDataSummer2017$ProjectType[surveyDataSummer2017$PostProject%in% c("Apache Spark", "KDevelop", "Mozilla", "RethinkDB", "Akka", "Vault")]<- "FOSS"
surveyDataSummer2017$ProjectType[surveyDataSummer2017$PostProject%in% c("MouseTrap")]<- "HFOSS"
surveyDataSummer2017$ProjectType[surveyDataSummer2017$PostProject%in% c("Job Match", "Ballzy", "Wanderlust", "eSport Connect", "Pocket TA","Mifos", "Bootstrap","Swift", "ReactJS","Xenon","Mousetrap", "Grading App", "Rate My Rental", "Automated User Tracking System", "VR Public Speaking Simulator", "Loop", "Brow Pro", "CSU Deals", "VRPS", "")]<-"Startup"
surveyDataSummer2017$ProjectType[surveyDataSummer2017$PostProject%in% c("RadioSTAR", "MESA Career Fair")]<- "LOCALORG"

```

Created another column that tells us whether or not the project was tech startup
```{r}

surveyDataSummer2017$IsTechStartUp[surveyDataSummer2017$ProjectType%in% c("Startup")]<- TRUE
surveyDataSummer2017$IsTechStartUp[surveyDataSummer2017$ProjectType%in% c("HFOSS","LFOSS","Industry", "FOSS", "Toy", "LOCALORG")]<- FALSE

```

Summary statistics of a variable by whether or not its a tech startup project.

Summary statistics of the variable PostBenefitSociety
```{r}
suppressWarnings(describeBy(surveyDataSummer2017$PostBenefitSociety, surveyDataSummer2017$IsTechStartup))
shapiro.test(surveyDataSummer2017$PostBenefitSociety)
```

Summary statistics of the variable PostAppreciateUsefulness
```{r}
suppressWarnings(describeBy(surveyDataSummer2017$PostAppreciateUsefulness, surveyDataSummer2017$IsTechStartup))
shapiro.test(surveyDataSummer2017$PostAppreciateUsefulness)
```

Summary statistics of the variable PostTeamInteractions
```{r}
suppressWarnings(describeBy(surveyDataSummer2017$PostTeamInteractions, surveyDataSummer2017$IsTechStartup))
shapiro.test(surveyDataSummer2017$PostTeamInteractions)
```

Summary statistics of the variable PostClientTechnical
```{r}
suppressWarnings(describeBy(surveyDataSummer2017$PostClientTechnical, surveyDataSummer2017$IsTechStartup))
shapiro.test(surveyDataSummer2017$PostClientTechnical)
```

Summary statistics of the variable PostClientBusiness
```{r}
suppressWarnings(describeBy(surveyDataSummer2017$PostClientBusiness, surveyDataSummer2017$IsTechStartup))
shapiro.test(surveyDataSummer2017$PostClientBusiness)
```

Summary statistics of the variable PostCSHelpPeople
```{r}
suppressWarnings(describeBy(surveyDataSummer2017$PostCSHelpPeople, surveyDataSummer2017$IsTechStartup))
shapiro.test(surveyDataSummer2017$PostCSHelpPeople)
```

Summary statistics of the variable PostInreaseComfortComputing
```{r}
suppressWarnings(describeBy(surveyDataSummer2017$PostIncreaseComfortComputing, surveyDataSummer2017$IsTechStartup))
shapiro.test(surveyDataSummer2017$PostIncreaseComfortComputing)
```

Summary statistics of the variable PostWelcomingHelpful
```{r}
suppressWarnings(describeBy(surveyDataSummer2017$PostWelcomingHelpful, surveyDataSummer2017$IsTechStartup))
shapiro.test(surveyDataSummer2017$PostWelcomingHelpful)
```

Summary statistics of the variable PostMaintainFOSS
```{r}
suppressWarnings(describeBy(surveyDataSummer2017$PostMaintainFOSS, surveyDataSummer2017$IsTechStartup))
shapiro.test(surveyDataSummer2017$PostMaintainFOSS)
```

Summary statistics of the variable PostBehaveProfessional
```{r}
suppressWarnings(describeBy(surveyDataSummer2017$PostBehaveProfessional, surveyDataSummer2017$IsTechStartup))
shapiro.test(surveyDataSummer2017$PostBehaveProfessional)
```

Summary statistics of the variable PostHighlyRelevant
```{r}
suppressWarnings(describeBy(surveyDataSummer2017$PostHighlyRevelant, surveyDataSummer2017$IsTechStartup))
shapiro.test(surveyDataSummer2017$PostHighlyRevelant)
```


